Golf-Sport: Managing Operations \\ A Case Study in Optimization

### 2018-05-08 Paper.tex
Final before Proofread
Code typesets successfully at this point.  Last stage of rough drafts, needs proofed and submitted

There is a clear need for operations management to be optimized, especially as a business or problem grows more complex. Several approaches for operations management use genetic algorithms, especially when focusing on lot sizing within material requirements, aggregate and assortment planning, and facility layout problems \cite{gen}.  
Additionally, particle swarm optimization methods have been successfully implemented into operations research problems.  Nearchou expands on this by stating that ``A possible reason for this absence is that, PSO was introduced as global optimizer over continuous spaces, while a large set of POM problems are of combinatorial nature with discrete decision variables" \cite{and}.  In short, he is declaring that the large scale nature of such production problems are indeed appropriate for PSO algorithms.  

@@

while they concluded that many operations management/production problems can be solved using linear programming, it may not always be the best approach.  However, by adjusting settings and parameters in software-based solvers, many large-scale problems can be effectively solved in this way \cite{klotz}.  This Golf-Sport problem falls squarely within the facilities management/production sector.  Fei et al discovered that for large-scale production optimizations, heuristics were necessarily utilized.  Additionally, the most common solution approaches utilize branch-and-cut or branch-and-price \cite{survey}.

@@

Besides component sales, the company takes the components and manufactures sets of golf clubs. Each set requires 13 shafts, 10 iron heads, and 3 wood heads. All of the shafts in a set must be the same type (steel or graphite), and all of the wood heads must be the same type (metal or metal with inserts). Each plant has unique assembly times.  Furthermore, each plant of Golf-Sport has a retail outlet to sell components and sets, and the specific plant is the only supplier for its retail outlet. The minimum and maximum amounts of demand for each plant–product pair are unique.

@@

The solution will presented as three options for production and sales: (1) manufactured and sold in month one; (2) manufactured and sold in month two; and (3) manufactured in month one and sold in month two. In this problem, two types of constraints exist: local and global. This two-month optimization can serve as a baseline and could later be expanded to more periods if desired. This particular problem appears to lend itself to integer programming as the ideal optimization method. The problem will be coded and solved using MATLAB’s optimization toolbox functionality.

@@

\section{Implementation}
\subsection{Hardware \& Software}
The problem was coded and solved in MATLAB R2017b on a personal computer.  The code does not appear to be backward-compatible due to the use of the \textit{optimproblem} implementation.  The small scale of this optimization does not necessitate a computer beyond average specifications.
\subsection{Algorithm}
This problem was solved using the \textit{intlinprog} function in MATLAB.  This function initially conducts a linear relaxation on the problem, in order to set the upper bound.  Then, the algorithm iterates through a branch-and-cut approach to solve for the optimal integer solution.  By default, the function 
will iterate through 1,000,000 iterations prior to terminating or until the gap tolerance is met.  These iterations check the feasible solutions at the nodes along the tree created through branch-and-bound.  Additionally, the function applies basic heuristics in the form of Gomory cuts.  Gomory cuts are defined as an added constraint along a hyperplane to a vertex.  They are commonly implemented in most commercial integer programming solvers as an initial heuristic.  In optimization software implementations, these cuts tend to be accurate overall and invalid cuts are rarely made \cite{gomory}.  Given this knowledge, it is safe to assume that these cuts will not negatively affect the solution to this problem.

\section{Solution}
The model was successfully optimized to the same solution over several runs, yielding the following optimal solution with constraints as laid out in the original problem above:
\\
\noindent
%begin{table}
\begin{tabular}{ l c c c }
\hline
\multicolumn{4}{|c|}{Optimal Chandler Production} \\
\hline
\textbf{Item} & \textbf{Period 1} & \textbf{Period 2} & \textbf{Period 1 Carryover} \\
Steel Shafts & 0 & 0 & 251 \\
Graphite Shafts & 100 & 2000 & 0 \\
Iron Heads & 200 & 0 & 200 \\
Metal Wood Heads & 35 & 1 & 30 \\
Titanium Insert Wood Heads & 2000 & 1299 & 701 \\
Set, Steel, Metal Heads & 0 & 0 & 0 \\
Set, Steel, Titanium Heads & 0 & 0 & 0 \\
Set, Graphite, Metal Heads & 0 & 0 & 0 \\
Set, Graphite, Titanium Heads & 0 & 35 & 84\\
\end{tabular}
%end{table} dont remove
\vspace{5mm}
\\
\noindent
%begin{table}
\begin{tabular}{ l c c c }
\hline
\multicolumn{4}{|c|}{Optimal Glendale Production} \\
\hline
\textbf{Item} & \textbf{Period 1} & \textbf{Period 2} & \textbf{Period 1 Carryover} \\
Steel Shafts & 0 & 0 & 0 \\
Graphite Shafts & 100 & 100 & 0 \\
Iron Heads & 200 & 199 & 1 \\
Metal Wood Heads & 36 & 30 & 6 \\
Titanium Insert Wood Heads & 2000 & 1289 & 711 \\
Set, Steel, Metal Heads & 0 & 0 & 0 \\
Set, Steel, Titanium Heads & 0 & 0 & 0 \\
Set, Graphite, Metal Heads & 0 & 0 & 0 \\
Set, Graphite, Titanium Heads & 0 & 68 & 83\\
\end{tabular}
%end{table} dont remove
\vspace{5mm}
\\
\noindent
%begin{table}
\begin{tabular}{ l c c c }
\hline
\multicolumn{4}{|c|}{Optimal Tucson Production} \\
\hline
\textbf{Item} & \textbf{Period 1} & \textbf{Period 2} & \textbf{Period 1 Carryover} \\
Steel Shafts & 1 & 0 & 2 \\
Graphite Shafts & 431 & 1265 & 2 \\
Iron Heads & 100 & 0 & 100 \\
Metal Wood Heads & 339 & 0 & 139 \\
Titanium Insert Wood Heads & 2000 & 814 & 1186 \\
Set, Steel, Metal Heads & 0 & 0 & 0 \\
Set, Steel, Titanium Heads & 0 & 0 & 0 \\
Set, Graphite, Metal Heads & 0 & 0 & 0 \\
Set, Graphite, Titanium Heads & 0 & 92 & 92\\
\end{tabular}
%end{table} dont remove
\\
\\
\vspace{5mm}
\\

@@

\section{Conclusions \& Implications}
\subsection{Mathematical Approach}
Mathematically speaking, the Golf-Sport case study was successfully modeled, coded, and solved.  Depending on the setup of the code, each run took between 13 seconds and 30 minutes for completion.  When the problem was modeled as a linear relaxation, solutions took seconds to be produced.  Solutions were effectively produced and passed spot testing on various constraints in an attempt to verify solution integrity.
\par
Critically viewed, the model was effective but perhaps inefficient, especially if extended beyond the two-month period under analysis.  From a retrospective viewpoint, the model could possibly have been developed with the variables as ``produced" and ``sold", eliminating the need for the ambiguous Period 3 connotation.  A model developed in this sense could be more easily expanded to more subsequent periods, increasing its utility to the organization.  It should be noted that these possible adjustments, however, would not produce any different results than what has been achieved in the current model.  An example of such a modifed objective function could be:
$$ f(x) = \sum Rs_{i,j} - \sum Cp_{i,j} - \sum I(p_{i,j}-s_{i,j}) $$
This function sets \textit{S} and \textit{P} as sold and produced items, with the difference between the two per period being the carryover inventory.
\par
In summary, the mathematical formulation and application on the Golf-Sport case study can be viewed as successful and easily modified to evaluate different parameters and constraints.
\subsection{Company Approach}
Upon completion of this analysis, it is evident that Golf-Sport can easily maximize their profit by utlizing such a model.  The parameters included, however, are superficial and unrealistic in many cases.  The problem modification above adjusts some constraints and adds to others, so as to help illustrate the process of developing a more complete picture of Golf-Sport operations.  While the actual numbers in the formulation are either arbitrary or unique to this case study, the modeling method utilized could be expanded and modified to fit many other production situations.

>>>>

There is a clear need for operations management to be optimized, especially as a business or problem grows more complex. Several approaches for operations management use genetic algorithms, especially when focusing on lot sizing within material requirements, aggregate and assortment planning, and facility layout problems.\cite{gen}  
Additionally, particle swarm optimization methods have been successfully implemented into operations research problems.  Nearchou expands on this by stating that ``A possible reason for this absence is that, PSO was introduced as global optimizer over continuous spaces, while a large set of POM problems are of combinatorial nature with discrete decision variables."\cite{and}  In short, he is declaring that the large scale nature of such production problems are indeed appropriate for PSO algorithms.  

@@

while they concluded that many operations management/production problems can be solved using linear programming, it may not always be the best approach.  However, by adjusting settings and parameters in software-based solvers, many large-scale problems can be effectively solved in this way.\cite{klotz}  This Golf-Sport problem falls squarely within the facilities management/production sector.  Fei et al discovered that for large-scale production optimizations, heuristics were necessarily utilized.  Additionally, the most common solution approaches utilize branch-and-cut or branch-and-price.\cite{survey}

@@

Besides component sales, the company takes the components and manufactures sets of golf clubs. Each set requires 13 shafts, 10 iron heads, and 3 wood heads. All of the shafts in a set must be the same type (steel or graphite), and all of the wood heads must be the same type (metal or metal with inserts). Each plant has unique assembly times.  Furthermore, each plant of Golf-Sport has a retail outlet to sell components and sets, and the specific plant is the only supplier for its retail outlet. The minimum and maximum amounts of demand for each location are unique.

@@

The solution will presented as three options for production and sales: (1) manufactured and sold in month one; (2) manufactured and sold in month two; and (3) manufactured in month one and sold in month two. In this problem, two types of constraints exist: local and global. This two-month optimization can serve as a baseline and could later be expanded to more periods if desired. This particular problem appears to lend itself to integer programming as the ideal optimization method. The problem will be coded and solved using MATLAB's optimization toolbox functionality.

@@

\section{Implementation}
\subsection{Hardware \& Software}
The problem was coded and solved in MATLAB R2017b on a personal computer.  The code does not appear to be backward-compatible due to the use of the \textit{optimproblem} implementation.  The small scale of this optimization does not necessitate a computer beyond average specifications.
\subsection{Algorithm}
This problem was solved using the \textit{intlinprog} function in MATLAB.  This function initially conducts a linear relaxation on the problem, in order to set the upper bound.  Then, the algorithm iterates through a branch-and-cut approach to solve for the optimal integer solution.  By default, the function 
will iterate through 1,000,000 iterations prior to terminating or until the gap tolerance is met.  These iterations check the feasible solutions at the nodes along the tree created through branch-and-bound.  Additionally, the function applies basic heuristics in the form of Gomory cuts.  Gomory cuts are defined as an added constraint along a hyperplane to a vertex.  They are commonly implemented in most commercial integer programming solvers as an initial heuristic.  In optimization software implementations, these cuts tend to be accurate overall and invalid cuts are rarely made.\cite{gomory}  Given this knowledge, it is safe to assume that these cuts will not negatively affect the solution to this problem.

\section{Solution}
The model was successfully optimized to the same solution over several runs, yielding the following optimal solution with constraints as laid out in the original problem above:
\\
\\
\\
\noindent
%begin{table}
\begin{tabular}{ l c c c }
\hline
\multicolumn{4}{|c|}{Optimal Chandler Production} \\
\hline
\textbf{Item} & \textbf{Period 1} & \textbf{Period 2} & \textbf{Period 1 Carryover} \\
Steel Shafts & 0 & 0 & 251 \\
Graphite Shafts & 100 & 2000 & 0 \\
Iron Heads & 200 & 0 & 200 \\
Metal Wood Heads & 35 & 1 & 30 \\
Titanium Insert Wood Heads & 2000 & 1299 & 701 \\
Set, Steel, Metal Heads & 0 & 0 & 0 \\
Set, Steel, Titanium Heads & 0 & 0 & 0 \\
Set, Graphite, Metal Heads & 0 & 0 & 0 \\
Set, Graphite, Titanium Heads & 0 & 35 & 84\\
\end{tabular}
%end{table} dont remove
\vspace{5mm}
\\
\noindent
%begin{table}
\begin{tabular}{ l c c c }
\hline
\multicolumn{4}{|c|}{Optimal Glendale Production} \\
\hline
\textbf{Item} & \textbf{Period 1} & \textbf{Period 2} & \textbf{Period 1 Carryover} \\
Steel Shafts & 0 & 0 & 0 \\
Graphite Shafts & 100 & 100 & 0 \\
Iron Heads & 200 & 199 & 1 \\
Metal Wood Heads & 36 & 30 & 6 \\
Titanium Insert Wood Heads & 2000 & 1289 & 711 \\
Set, Steel, Metal Heads & 0 & 0 & 0 \\
Set, Steel, Titanium Heads & 0 & 0 & 0 \\
Set, Graphite, Metal Heads & 0 & 0 & 0 \\
Set, Graphite, Titanium Heads & 0 & 68 & 83\\
\end{tabular}
%end{table} dont remove
\vspace{5mm}
\\
\noindent
%begin{table}
\begin{tabular}{ l c c c }
\hline
\multicolumn{4}{|c|}{Optimal Tucson Production} \\
\hline
\textbf{Item} & \textbf{Period 1} & \textbf{Period 2} & \textbf{Period 1 Carryover} \\
Steel Shafts & 1 & 0 & 2 \\
Graphite Shafts & 431 & 1265 & 2 \\
Iron Heads & 100 & 0 & 100 \\
Metal Wood Heads & 339 & 0 & 139 \\
Titanium Insert Wood Heads & 2000 & 814 & 1186 \\
Set, Steel, Metal Heads & 0 & 0 & 0 \\
Set, Steel, Titanium Heads & 0 & 0 & 0 \\
Set, Graphite, Metal Heads & 0 & 0 & 0 \\
Set, Graphite, Titanium Heads & 0 & 92 & 92\\
\end{tabular}
%end{table} dont remove
\\
\\
\vspace{5mm}
\\

@@

\section{Conclusions \& Implications}
\subsection{Mathematical Approach}
Mathematically speaking, the Golf-Sport case study was successfully modeled, coded, and solved.  Depending on the setup of the code, each run took between 13 seconds and 30 minutes for completion.  When the problem was modeled as a linear relaxation, solutions took seconds to be produced.  Solutions were effectively produced and passed spot testing on various constraints in an attempt to verify solution integrity.
\par
Critically viewed, the model was effective but perhaps inefficient, especially if extended beyond the two-month period under analysis.  From a retrospective viewpoint, the model could possibly have been developed with the variables as ``produced" and ``sold", eliminating the need for the ambiguous Period 3 connotation.  A model developed in this sense could be more easily expanded to more subsequent periods, increasing its utility to the organization.  It should be noted that these possible adjustments, however, would not produce any different results than what has been achieved in the current model.  An example of such a modifed objective function could be:
$$ f(x) = \sum Rs_{i,j} - \sum Cp_{i,j} - \sum I(p_{i,j}-s_{i,j}) $$
This function sets \textit{s} and \textit{p} as sold and produced items, with the difference between the two per period being the carryover inventory.
\par
In summary, the mathematical formulation and application on the Golf-Sport case study can be viewed as successful and easily modified to evaluate different parameters and constraints.
\subsection{Company Approach}
Upon completion of this analysis, it is evident that Golf-Sport can easily maximize their profit by utilizing such a model.  The parameters included, however, are superficial and unrealistic in many cases.  The problem modification above adjusts some constraints and adds to others, so as to help illustrate the process of developing a more complete picture of Golf-Sport operations.  While the actual numbers in the formulation are either arbitrary or unique to this case study, the modeling method utilized could be expanded and modified to fit many other production situations.  Some possible other questions that can be explored in the future using such a model and case could be:
\begin{itemize}
	\item When does is become feasible to open a new plant or expand an existing one?
	\item How does eliminating certain products (e.g. steel shafts) impact sales? Does it increase profit by shifting the customer base to another product? Can Golf-sport handle the increased demand of the other products?
	\item How does the shifting cost of materials (other than graphite) change what is produced? How does it impact profits?
	\item What do profits look like when evaluating beyond a two-month period?
\end{itemize}
In short, the current model can be expanded on in many different directions depending on the goal of the analysis.  It is by this measure that this optimization approach can be deemed successful, as continuing analysis is of paramount importance in operations management.
